Consistency and Fault Tolerance Considerations for the Next Iteration of the DOE Fast Forward Storage and IO Project

### 2014-03-21 paper.tex
incorporated comments from call today

The basic architecture incorporates five layers. The top layer is a high level
IO library, such as the demonstration HDF-5 library~\cite{hdf5}. The intent is to only have
access to the storage stack through such an API to manage the complexity of
working with the lower layers. Below the user API is an IO forwarding layer
that redirects IO calls from the compute nodes to the IO dispatching layer.
This IO forwarding layer is analogous to the function of the IO nodes in a
BlueGene machine. The next two layers have considerable functionality. The IO
dispatcher (IOD) serves as the primary storage interface for the IO stack and
is the only way to reach the persistent storage array in lower layers. The
Data Access Object Storage (DAOS) layer serves as the persistent storage
interface. At the bottom is the Versioning Object Storage Device (VOSD). It
serves as the interface for storing objects of all types efficiently.

@@

Along with the analysis of the published design documents, a discussion of the
design philosophy representing the overall intent is presented. This
information represents information that may or may not have been written down,
but is the intent of ultimate product. These insights were gained based on
personal conversations with the team members discussing some of the potential
challenges with the design as written. These ideas are presented to give a
fuller picture of where the project is going rather than dwelling on the
limitations of the published documents.

@@

The idea of burst buffers were initially explored in the context of data
staging~\cite{abbasi:2007:datatap,Abbasi:2009:datatap,nisar:2008:staging,zheng:2010:predata}.
These initial designs all use extra compute nodes to represent the data storage
buffer given the lack of any dedicated hardware support for this functionality.
The desired outcome of these initial studies is to motivate how such
functionality might be incorporated and the potential benefits.  Later, these
concepts were proposed to be incorporated as part of the IO
stack~\cite{nowoczynski:2008:zest,bent:2012:challenges,bent:2012:burst-buffer}.
The current FastForward IOD design recommends incorporating SSDs, but
specifically lists these devices as optional. Unfortunately, not incorporating
burst buffers and the use of SSDs in the IOD layer may be problematic.  First,
the IOD and DAOS designs currently are written assuming burst buffers. This
means that the bulk of IO operations will only hit the IOD layer and proposed
functionality, such as the function shipping, do not discuss the impact on the
DAOS layer or the operators themselves should a burst buffer not be available.
Consider the important functionality of data rearrangement and doing things
like changing the fast array dimension on shared, spinning media.  The design
of DAOS assumes that it will only be involved when persisting a completed
transaction and only for a fraction of the total transactions created.
Transaction frequency at the IOD layer can be higher since IOD does not
``flatten'' transactions. Flattening is the process of making each transaction
fully-independent by duplicating any data unchanged from previous transactions.
DAOS epochs are persisted, flattened transactions from the IOD layer.

@@

By concentrating the Burst Buffers and function shipping into the storage
stack, three problems arise.  First, the amount of network bandwidth, IO
bandwidth, and compute power consumed for example operations from a single
application is likely to completely monopolize the IOD processes. Second, if
space and time partitioning is used instead, the functionality risks being too
small to be useful. Third, the hardware performance advantage for SSDs is
questionable. Current NAND-based flash devices top out at around 400 MB/sec.
The key spec that is missing from this number is that 400 MB/sec is a measure
of the fixed number of available IOPS multiplied by the block size. This
represents the ideal streaming performance possible. The problem is that it
costs an IOP to read 1 byte or 1 block (4KB or 8KB, depending on the device).
It costs 1 IOP to write a full block--usually. In some cases, it will cost 2
IOPs.  This accounts for the required pre-erase write prior to writing to a
reused block. In the worst case, it can be 3 IOPS per write. This would be for
a partial block write (read the old block, erase, write the modified block).
One-third of 400 MB/sec, about 133 MB/sec, is well below the streaming
performance of HDDs.  Granted, there is still rotational and seek latency to
deal with for HDDs, but the advantage for SSDs has evaporated and potentially
turned into a penalty at a considerable cost premium.  There are faster SSD
solutions on the market that incorporate DRAM for caching and using the PCIe
bus, for example, but their price precludes them from use in an extreme scale
platform.

@@

\subsection{Design Philosophy}
The burst buffers design, as presented in the IOD documents, limits the
placement of the function operators and SSD buffers to the IO nodes. The team
does acknowledge the limitations of this design and intend to ultimately focus
on spreading the IOD layer from the IO nodes into the compute area as well.
This is intended both to help address the limitations of the IO bandwidth and
compute capability of these few nodes for data processing, but also to take
advantage of new layers in the storage hierarchy. By incorporating NVRAM into
compute nodes, new options for buffering data prior to being moved to
centralized storage become available and addresses some of the concerns about
SSD performance. This lessens the impact of some operators while offering
additional options for places to store data.

@@

Another concern that is acknowledged, but no thought has been applied to, is
the requirement that a single IOD process be the master for any operation.
Should the number of concurrent applications exceed the available nodes,
sharing an IOD process will be required. Since partitioning of the IOD
processes for exclusive use by particular applications is the assumed operating
mode, should insufficient IOD resources be available, either a job could be
delayed or IOD resources could be reallocated from a different process could be
redeployed for use by the new job. Handling resilience concerns for the IOD
processes must also be address. These sorts of considerations still need to be
made for a full production system.

@@

The transaction mechanism manifests in two forms. At the IOD layer, they are
called transactions and are used to judge whether or not a set of distributed,
asynchronous modifications across a set of related objects is complete or not
and control access through treating the transaction ID of committed transaction
as a version identifier.  At the DAOS layer, they are called epochs and
represent persisted (durable) transactions from the IOD layer. Each of these
offers different functionality, but are connected as is explained below. How
these differ from the \DDT approach is also explored. While IOD's and \DDTns's
transactions are seemingly very different, they use a similar high-level
design, but very different implementation, to solve the same problem.

\subsection{IOD Transactions}
To understand how transactions are used in the IOD layer, some terminology and
concepts must be explained first. At the coarsest grain level is a container.
Each container serves to host a transaction and contains a collection of
objects. Conceptually, containers corresponds to a file in a traditional file
system. The objects in each container represent different data within a file.
The three initially defined object types are key-value stores,
multi-dimensional arrays, and blobs.  The easiest way to understand these types
is to evaluate these from the perspective of an HDF-5 file, the initial user
interface layer. The key-value store represents a collection of attributes or
groups. The array represents part of a potentially multi-dimensional array. It
is referred to as a shard because it is likely a small piece of a globally
defined array. The blob represents a byte stream of arbitrary contents.  The
fundamental difference between an array and a blob is that the array has
metadata identifying its portion within the global, logical space while the
blob is simply a 1-dimensional array of bytes that is not shared across IOD
nodes.  Should an operation be deployed into IOD to manipulate an array within
a container, it would operate on the array rather than on blobs. Given this
context, the transactions come in two forms.

@@

The team uses the term ``Primary'' to define the process(es) that contact the
IOD layer directly to open a container. Unfortunately, this term is never used
nor defined within any of the published documents. There are some very positive
and negative performance implications of this approach. On the positive side,
like PVFS, it is possible for a single process to open a container and share
that handle with other processes reducing the load on the IOD layer. The key
idea is that the single leader vs. multi-leader transaction mode is
automatically defined based on the number of Primary processes that start a
transaction on a container. This greatly simplifies any additional client-side
load in using the different styles of transactions. Also on the positive side,
it offers the ability to have a subset of processes that are considered
transaction participants affording reduced load on the IOD processes and more
localized transaction management on the client side. On the negative side, for
a fully IOD managed transaction, ALL processes must start the transaction on
the container forcing a potentially immense number of simultaneous calls to the
IOD layer to open a container. This sort of onslaught is what is dealt with on
metadata servers today with mass file opens. The reality is that this ends up
having the same sort of performance implications as distributed denial of
service attacks on the IOD processes.

Ultimately, with the passive detection of faults for Primaries, the transaction
mechanism can work very well. A mostly unstated restriction that is being
relaxed is that every sequential transaction on a container is considered
dependent on the earlier transaction. Should one output be delayed and the
subsequent five succeed, when the delayed process finally fails, all six
transactions are rolled back. The thought of using this mechanism to store
subsequent checkpoint outputs in the same container to both save space, but not
care if one fails, cannot work in the current form. This has been acknowledged
and is planned on being relaxed in phase two.

@@

\subsection{Metadata Management}
Eliminating metadata management as a special case and instead treating it just
as data is a central design goal of the Fast Forward project. This is a hybrid
approach to metadata management that is half-way between providing no inherent
metadata support and having a fully integrated, but separate metadata
manaegement system.

@@

IOD and DAOS both share a philosophy that they will have to maintain the
metadata about how objects are striped and where they are placed. It was
decided that the additional data to track the namespace as well was a small
enough additional increment that it was worth maintaining within the system.

\subsubsection{Design Philosophy}
While the metadata design is not fully defined, there are a few things that
are intended. For example, there is a standard, well-known container that is
the system metadata. This includes the list of all other containers. This
container is treated like any other data in the system and striped as
appropriate at both the IOD and the DAOS layers. Unfortunately, this still
couples the metadata to a single object that must serialize access. If the
metadata, including information about striping and other data layout operations
were separated completely from the data path, more scalable throughput could be
achieved. The real challenge of this is introduced by the IOD, DAOS, and VOSD
layers. Each of these requires some different metadata storage and the
migration is transparent to the user. Supporting fully independent metadata
with this model is difficult. Serious thought on how to do this effectively
outside the data path should be considered for phase two.

@@

The second iteration of the protocol~\cite{lofstead:2013:pdsw-txn} fixed
scalability issues and demonstrated a scalable client-side coordination model
with excellent performance. The performance measured for a complex transaction
with \DDT is illustrated in Figure~\ref{fig:performance}. This performance is
explored in detail in a previous paper~\cite{lofstead:2013:pdsw-txn}. The
breakdown of the number of participants in each role is shown in
Table~\ref{tab:scaling}. For comparison, consider the Number of
Sub-Coordinators equivalent to IOD processes. The Processes Per Sub-Coordinator
represents the number of clients that use a particular IOD process. For these
tests, we maintained a balanced distribution and always used at least two
sub-coordinators to slow down the processing.

@@

\begin{table}[ht]
    \vspace{-0.15in}
    \centering
    \caption[Scaling Configuration]{Performance Tests Scaling Configuration}
    \bigskip
    \vspace{-0.15in}

    \begin{tabular}{|r|r|r|}
\hline
Processes & \vtop{\hbox{\strut Number of}\hbox{\strut Sub-Coordinators}} & \vtop{\hbox{\strut Processes Per} \hbox{\strut Sub-Coordinator}}\\
\hline
%8 & 2 & 4 \\
%16 & 2 & 8 \\
%32 & 2 & 16 \\
%64 & 2 & 32 \\
%128 & 2 & 64 \\
256 & 2 & 128 \\
512 & 2 & 256 \\
1024 & 4 & 256 \\
2048 & 8 & 256 \\
4096 & 16 & 256 \\
8192 & 32 & 256 \\
16384 & 64 & 256 \\
32768 & 128 & 256 \\
65536 & 256 & 256 \\
\hline
    \end{tabular}
    \label{tab:scaling}
\end{table}

@@

In the multi-leader model, using a count of client connections to determine if
transaction is complete is problematic. First, the aggregation of completion
messages are based on the local aggregation point reporting to the transaction
leader.  There is no ability to detect or recover from a failure of this IOD
process that would report to the transaction leader. The current assumption
that the IOD layer will be an MPI program is not workable until MPI can fully
support fault detection and recovery including removing and adding processes.
Second, since the counts represent a begin/end transaction pair, it suffers
from a lack of accountability for missing object (shard) writes. All it would
indicate is that a process started and ended a transaction connection. There is
no validation that a process has done everything required of it.

\begin{figure}[ht]
\centering
\includegraphics[keepaspectratio=true, width=0.9\columnwidth]{images/optimized-protocol}
\vspace{-0.15in}
\caption{Optimized Protocol}
\label{fig:optimized-protocol}
%\vspace{-0.25in}
\end{figure}

@@

\section{Acknowledgements}
The authors would like to thank Gary Grider, Eric Barton, Quincey Koziol, and
John Bent for their early review comments and discussions that clarified the
details of the design, the intent of the design, and the future plans.

>>>>

The basic architecture incorporates five layers. The top layer is a high level
IO library, such as the demonstration HDF-5 library~\cite{hdf5}. The intent is
to only have access to the storage stack through such an API to manage the
complexity of working with the lower layers. Below the user API is an IO
forwarding layer that redirects IO calls from the compute nodes to the IO
dispatching layer.  This IO forwarding layer is analogous to the function of
the IO nodes in a BlueGene machine. The next two layers have considerable
functionality. The IO dispatcher (IOD) serves as the primary storage interface
for the IO stack and is the only way to reach the persistent storage array in
lower layers. The Data Access Object Storage (DAOS) layer serves as the
persistent storage interface and is intended to be the foundation on which
everything else is built with no dependence on any technologies specified above
it. For example, the IOD layer and burst buffers are not required for DAOS to
operate properly. At the bottom is the Versioning Object Storage Device (VOSD).
It serves as the interface for storing objects of all types efficiently.

@@

Along with the analysis of the published design documents, a discussion of the
design philosophy representing the overall intent is presented. This
information represents information that may or may not have been written down,
but is the intent of ultimate product. These insights were gained based on
personal conversations with the team
members~\cite{JohnBent,QuinceyKoziol,EricBarton} discussing some of the
potential challenges with the design as written. These ideas are presented to
give a fuller picture of where the project is going rather than dwelling on the
limitations of the published documents.

@@

The idea of burst buffers were initially explored in the context of data
staging~\cite{abbasi:2007:datatap,Abbasi:2009:datatap,nisar:2008:staging,zheng:2010:predata}.
These initial designs all use extra compute nodes to represent the data storage
buffer given the lack of any dedicated hardware support for this functionality.
The desired outcome of these initial studies is to motivate how such
functionality might be incorporated and the potential benefits.  Later, these
concepts were proposed to be incorporated as part of the IO
stack~\cite{nowoczynski:2008:zest,bent:2012:challenges,bent:2012:burst-buffer}.
The current FastForward IOD design recommends incorporating SSDs, but
specifically lists these devices as optional. Unfortunately, not incorporating
burst buffers and the use of SSDs in the IOD layer may be problematic.  First,
the IOD and DAOS designs currently are written assuming burst buffers. This
means that the bulk of IO operations will only hit the IOD layer and proposed
functionality, such as the function shipping, do not discuss the impact on the
DAOS layer or the operators themselves should a burst buffer not be available.
Consider the important functionality of data rearrangement and doing things
like changing the fast array dimension on shared, spinning media.  The design
of DAOS assumes that it will only be involved when persisting a completed
transaction and only for a fraction of the total transactions created.
Transaction frequency at the IOD layer can be higher since IOD does not
``flatten'' transactions. Flattening is the process of transfering the set of
copy-on-write changes from transaction/epoch $n$ to transaction $n+m$ into the
DAOS layer. The DAOS layer mirrors the copy-on-write functionality, but stores
the differences between epochs rather than individual transactions. The primary
difference is that at the DAOS layer, data is stored in large, logically
contiguous chunks to manage the metadata load and hopefully improve read
performance.

@@

By concentrating the Burst Buffers and function shipping into the storage
stack, three problems arise.  First, the amount of network bandwidth, IO
bandwidth, and compute power consumed for example operations from a single
application is likely to completely monopolize the IOD processes. Second, if
space and time partitioning is used instead, the functionality risks being too
small to be useful. Third, the long-term hardware performance advantage for
SSDs is questionable. Recent studies have shown that the erase-before-write
and interference between reading and writing with flash-based SSDs can cause
severe performance problems~\cite{skourtis:2013:ssd-performance}. The inclusion
of an optional use SSD layer in the new Trinity machine at Los Alamos will
offer a testbed to determine how likely these observed problems would affect a
production extreme scale platform.

%Current NAND-based flash devices top out at around 400 MB/sec.
%The key spec that is missing from this number is that 400 MB/sec is a measure
%of the fixed number of available IOPS multiplied by the block size. This
%represents the ideal streaming performance possible. The problem is that it
%costs an IOP to read 1 byte or 1 block (4KB or 8KB, depending on the device).
%It costs 1 IOP to write a full block--usually. In some cases, it will cost 2
%IOPs.  This accounts for the required pre-erase write prior to writing to a
%reused block. In the worst case, it can be 3 IOPS per write. This would be for
%a partial block write (read the old block, erase, write the modified block).
%One-third of 400 MB/sec, about 133 MB/sec, is well below the streaming
%performance of HDDs.  Granted, there is still rotational and seek latency to
%deal with for HDDs, but the advantage for SSDs has evaporated and potentially
%turned into a penalty at a considerable cost premium.  There are faster SSD
%solutions on the market that incorporate DRAM for caching and using the PCIe
%bus, for example, but their price precludes them from use in an extreme scale
%platform.

@@

\subsection{Design Philosophy}
The burst buffers design, as presented in the IOD documents, limits the
placement of the function operators and SSD buffers to the IO nodes. The team
does acknowledge the limitations of this design and intend to ultimately focus
on spreading the IOD layer from the IO nodes into the compute area as well.
This is intended both to help address the limitations of the IO bandwidth and
compute capability of these few nodes for data processing, but also to take
advantage of new layers in the storage hierarchy. By incorporating NVRAM into
compute nodes, new options for buffering data prior to being moved to
centralized storage become available and addresses some of the concerns about
SSD performance. For example, including a small amount of Phase Change memory
into many or most compute nodes offers a way to move data outside of both the
compute and IO path for data and communication intensive operations. Other 
projects~\cite{zheng:2010:predata} have suggested this will have value, but the
cost will have to be considered as part of the overall platform budget. This
lessens the impact of some operators while offering additional options for
places to store data.

@@

Another concern that is acknowledged, but no thought has been applied to, is
the requirement that a single IOD process be the master for any operation.
Should the number of concurrent applications exceed the available nodes,
sharing an IOD process will be required. The requirements both in terms of
scheduling and resource management were cut from the project due to funding
limitations. Since partitioning of the IOD processes for exclusive use by
particular applications is the assumed operating mode, should insufficient IOD
resources be available, either a job could be delayed or IOD resources could be
reallocated from a different process could be redeployed for use by the new
job. Handling resilience concerns for the IOD processes must also be address.
These sorts of considerations still need to be made for a full production
system.

@@

The transaction mechanism manifests in two forms. At the IOD layer, they are
called transactions and are used to judge whether or not a set of distributed,
asynchronous modifications across a set of related objects is complete or not.
It is also used to control access by treating the transaction ID of committed
transaction as a version identifier.  At the DAOS layer, they are called epochs
and represent persisted (durable) transactions from the IOD layer. Each of
these offers different functionality, but are connected as is explained below.
How these differ from the \DDT approach is also explored.  While IOD's and
\DDTns's transactions are seemingly very different, they use a similar
high-level design, but very different implementation, to solve the same
problem.

\subsection{IOD Transactions}
To understand how transactions are used in the IOD layer, some terminology and
concepts must be explained first. At the coarsest grain level is a container.
Each container provides the single access context through which to access a
collection of objects. Transactions are the way that a series of modifications
to the objects within a container are treated atomically. Conceptually,
containers corresponds to a something akin to an HDF5 file in a traditional
file system. The objects in each container represent different data within a
file.  The three initially defined object types are key-value stores,
multi-dimensional arrays, and blobs.  The easiest way to understand these types
is to evaluate these from the perspective of an HDF-5 file, the initial user
interface layer. The key-value store represents a collection of attributes or
groups. The array represents a potentially multi-dimensional array.  The blob
represents a byte stream of arbitrary contents.  The fundamental difference
between an array and a blob is that the array has metadata specifying the
dimension(s). At the physical layer within the IO nodes, all of these objects
may be striped across multiple IO nodes.  Given this context, the transactions
come in two forms.

@@

There are two steps for beginning a transaction on a container. The first step
is for one or more process to open the container. This handle can be shared
eliminating the need for every participating process to hit the IOD layer to
open the file. The second step is a call to determine how many leaders will
participate in the transaction. In the single leader case, there is no
aggregation of success/fail statuses to determine the final transaction state.
Instead, it is assumed that the client will fully manage the transaction. In
the multi-leader model, some subset from 2 to $n$ where $n$ is the count of all
processes, declare themselves a leader for this container operation to the IOD
layer. Any number of processes can participate in modifying container without
regard to whether or not they are a leader. Once each leader has finished, with
the assumption that any clients they may be responsible for are finished as
well, the IOD layer aggregates those responses to either commit or abort the
transaction.

Ultimately, with the passive detection of faults for transaction leaders, the
transaction mechanism can work very well. A mostly unstated restriction that is
being relaxed is that every sequential transaction on a container is considered
dependent on the earlier transaction. Should one output be delayed and the
subsequent five succeed, when the delayed process finally fails, all six
transactions are rolled back. The thought of using this mechanism to store
subsequent checkpoint outputs in the same container to both save space, but not
care if one fails, cannot work in the current form. This has been acknowledged
and is being relaxed requiring a new parameter to the creation of a transaction
determining if it will be dependent or not.

@@

\subsection{Metadata Management}
Metadata management has been a perennial challenge for parallel storage
systems.  Eliminating metadata management as a special case and instead
treating it just as data is a central design goal of the Fast Forward project.
This is a hybrid approach to metadata management that is half-way between
providing no inherent metadata support and having a fully integrated, but
separate metadata manaegement system.

@@

IOD and DAOS both share a philosophy that they will have to maintain the
metadata about how the physical pieces of the logical objects are striped and
where they are placed. The primary metadata management is done at the DAOS
layer with the IOD layer relying on the DAOS layer for all authoritative
information about containers and objects. The only place where the IOD layer
manages metadata for itself is to manage how the different objects are striped
across the IO nodes.

\subsubsection{Design Philosophy}
While the metadata design is not fully defined, there are a few things that
are intended. For example, there is a standard, well-known container that is
the system metadata. This includes the list of all other containers. This
container is treated like any other data in the system and striped as
appropriate. Unfortunately, this still couples the metadata to a single object
that must serialize access. If the metadata, including information about
striping and other data layout operations were separated completely from the
data path, more scalable throughput could be achieved. The real challenge of
this is introduced by the IOD, DAOS, and VOSD layers collectively. Each of
these requires some different metadata storage and the migration is transparent
to the user.  Supporting fully independent metadata with this model is
difficult. Serious thought on how to do this effectively outside the data path
should be considered for phase two.

@@

The second iteration of the protocol~\cite{lofstead:2013:pdsw-txn} fixed
scalability issues and demonstrated a scalable client-side coordination model
with excellent performance. The performance measured for a complex transaction
with \DDT is illustrated in Figure~\ref{fig:performance}. This performance is
explored in detail in a previous paper~\cite{lofstead:2013:pdsw-txn}.
%The
%breakdown of the number of participants in each role is shown in
%Table~\ref{tab:scaling}. For comparison, consider the Number of
%Sub-Coordinators equivalent to IOD processes. The Processes Per Sub-Coordinator
%represents the number of clients that use a particular IOD process. For these
%tests, we maintained a balanced distribution and always used at least two
%sub-coordinators to slow down the processing.

@@

%\begin{table}[ht]
%    \vspace{-0.15in}
%    \centering
%    \caption[Scaling Configuration]{Performance Tests Scaling Configuration}
%    \bigskip
%    \vspace{-0.15in}
%
%    \begin{tabular}{|r|r|r|}
%\hline
%Processes & \vtop{\hbox{\strut Number of}\hbox{\strut Sub-Coordinators}} & \vtop{\hbox{\strut Processes Per} \hbox{\strut Sub-Coordinator}}\\
%\hline
%%8 & 2 & 4 \\
%%16 & 2 & 8 \\
%%32 & 2 & 16 \\
%%64 & 2 & 32 \\
%%128 & 2 & 64 \\
%256 & 2 & 128 \\
%512 & 2 & 256 \\
%1024 & 4 & 256 \\
%2048 & 8 & 256 \\
%4096 & 16 & 256 \\
%8192 & 32 & 256 \\
%16384 & 64 & 256 \\
%32768 & 128 & 256 \\
%65536 & 256 & 256 \\
%\hline
%    \end{tabular}
%    \label{tab:scaling}
%\end{table}

@@

The multi-leader model introduces the possibility of forcing a rollback of an
entire transaction when a partial retry might be sufficient for success. Since
the transactions are managed at a high level rather than the individual
tasks, a failure in a limited distributed task can cause the entire transaction
to fail. For example, consider 10 processes each have 5 tasks, but 3 of those
10 have an additional shared task to complete. If the task shared by the 3
processes fails on any of the three, the entire transaction would roll back
because it is a coarse-grained success/failure. If a concept like
sub-transactions at a task granularity were used, then it would be possible for
the one process that failed to report just that failure. Then the transaction
manager could reassign the resources for these 3 processes and try just that
operation again. If it now succeeds, then the overall transaction can be marked
successful only redoing the minimum amount of work required.

\begin{figure}[ht]
\centering
\includegraphics[keepaspectratio=true, width=0.5\columnwidth]{images/optimized-protocol}
\vspace{-0.15in}
\caption{Optimized Protocol}
\label{fig:optimized-protocol}
%\vspace{-0.25in}
\end{figure}

@@

\section{Acknowledgements}
The authors would like to thank Eric Barton, John Bent, Gary Grider, and
Quincey Koziol for their early review comments and discussions that clarified
the details of the design, the intent of the design, and the future plans.
